---
title: "R Project 1 - Hello R"
author: "Ashly Garcia"
date: "9/16/2020"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen file has 1846 rows and 3 columns. It includes a total of 3 variables which are the dataset (labels from which dataset the data is taken from), x (x-values) and y(y-values).

### Exercise 2
First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Now, we will reuse the code chunk in lines 26-29 in order to plot the x vs. y for the "star" dataset, and visualize the correlation between the two variables for the star dataset.

```{r plot-star}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

Next, we can calculate "r" (the correlation coefficient) for the "star" data set to see how it compares to that of the "dino" dataset from Exercise 2.
 
```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))
```
Through this calculation, we can see that the r value between x and y in the "star" dataset is slightly closer to -1 that of  x and y from the "dino" dataset. Remember, both datasets show a negative r-value (correlation coefficient) between x and y, however, one is closer to -1 than the other. Since the r value from the "star" dataset is closer to -1, this means the negative correlation between x and y in the "star" dataset is stronger than within the "dino" dataset.

### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

```{r}


```

```{r}


```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)